Query Optimization for Dynamic Imputation

### 2017-07-03 paper/algorithm.tex
paper: tweak definition of alpha bound optimal

\begin{definition}
Let $Q$ be a set of plans. For $q \in Q$, we say $q$ is $\alpha$-bound, if $(\textsc{Penalty}(q) - \min_{q' \in Q}(\textsc{Penalty}(q')) \leq \alpha$. We denote this as $q^\alpha$.
We define the set of $\alpha$-bound plans in $Q$ as $Q^\alpha$.
We say a plan $q^\alpha$ is $\alpha$-bound optimal if $\forall q' \in Q^\alpha. \textsc{Time}(q) \leq \textsc{Time}(q')$. 
\end{definition}

>>>>

\cameraready{
\begin{definition}
Let $Q$ be a set of plans. For $q \in Q$, we say $q$ is $\alpha$-bound if \[\textsc{Penalty}(q) - \min_{q' \in Q} \textsc{Penalty}(q') \leq \alpha.\] We denote this as $q^\alpha$.
Let the set of $\alpha$-bound plans in $Q$ be $Q^\alpha$.
We say a plan $q^\alpha$ is $\alpha$-bound optimal if \[\textsc{Time}(q^\alpha) = \min_{q' \in Q} \textsc{Time}(q').\]
\end{definition}
}
